\normalfont\spacedallcaps{Hazardous asteroids forecast via Markov random fields}

### 2021-11-24 Manuscript/manuscript.tex
PU

Finally the \textcolor{red}{Absolute magnitude} $M$ can be defined as the magnitude that the item will have if it is put at 1 AU\footnote{Astronomic Units, the distance between Earth and Sun: 1.49\cdot 10^{11} m} or 10 parsec \footnote{3,08\cdot 10^{16} m. The physical meaning of this measure can be found in \cite{burbine2016asteroids}} from the observer. Therefore  \cite{burbine2016asteroids}:

@@

>>>>

Finally the \textcolor{red}{Absolute magnitude} $M$ can be defined as the magnitude that the item will have if it is put at 1 AU\footnote{Astronomic Units, the distance between Earth and Sun: 1.49\cdot 10^{11} m} or 10 parsec \footnote{$3,08\cdot 10^{16}$ m. The physical meaning of this measure can be found in \cite{burbine2016asteroids}} from the observer. Therefore  \cite{burbine2016asteroids}:

@@

\section{Classification}

The solar system is composed not only by planets and the Sun, but also by a plethora of small bodies\footnote{Small with respect to the size of planets} whose orbit can be near to the Earth \cite{burbine2016asteroids}. In particular if the orbit of these items is near less then 1.3 AU such items are called near-Earth object (NEO). Such items are of three type: comets, meteoroids and asteroids. The first one are icy bodies that moving near the sun melts and release gases giving coloured tails. Meteroids are small \footnote{With respect to asteroids} rocky/metallic items with a diameter less than 1 meter. Asteroids, on the other side, are items with a diameter larger than 1 m \cite{burbine2016asteroids}. The first two items are excluded from the present analysis.  
The near asteroids are classified, as shown in Fig. \ref{neo_orbit_types}, according to their semi-major axis, perihelion distance, and aphelion distance \cite{nasa_classification}:

\begin{itemize}
\item \textbf{Atiras}
\item \textbf{Atens}
\item \textbf{Apollos}
\item \textbf{Amors}
\end{itemize}

\begin{figure}[h]
\begin{center}
\includegraphics[width=1\textwidth]{Figures/neo_orbit_types.jpg}
\caption{NASA classification of NEO asteroids accompained by the legend for the parameters a,q and Q. Image taken from \cite{nasa_classification}}
\label{neo_orbit_types}
\end{center}
\end{figure}
